---
title: "Rmarkdown"
author: "Viktoriia Tantsiura, Valeriia Zinoveva, Mercédesz Lehoczky"
date: "2023-03-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, 
  warning = FALSE, 
  message = FALSE, 
  dpi = 300)
```

# Setup

## Load libraries

```{r}
library(tidyverse)
```

## Load data

```{r}
data <- read.csv("data/insurance.csv")
data
```

# Data exploration

## Data dimensions

```{r}
dim(data)
```

## Data structure

```{r}
str(data)
```
#Test the empirical hypothesis. 

## Data cleaning

```{r}
data_c <- data %>% 
  filter(sex == "female") %>% 
  mutate(Group = ifelse(age >= 35, "Above 35", "Below 35"))
data_c
```

## Women in each group

```{r}
data_c %>% 
  count(Group)
```


## Visualization

```{r}
data_c %>% 
  ggplot(aes(x = Group, y = charges, color = Group)) +
  geom_boxplot() +
  labs(x = NULL, y = "Charges ($)", color = "Age") +
  theme_bw()
```


## T-test

```{r}
t.test(charges ~ Group, data = data_c, alternative = "greater")
```

#Research question.

- Do females spend more money on insurance after age of 35?


##Empirical hypothesis addressing the research question. 

Elder women (Age > 35) are likely to pay more on insurance. There, we hypothesize .....


$H_0$ = Females after age 35 spend less than or same amount of money as females before 35 age
$H_a$ = Females after age 35 spend more money than females before 35 age

